Playing Games: A Case Study in Active Learning Applied to Game Theory

### 2015-06-30 paper/paper.tex
Adding image of white board.

\usepackage[backend=biber,firstinits=true , backref=false, url=true, isbn=true]{biblatex}
\addbibresource{library.bib}

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}
            % First level of play
            \node (0) at (0,0) {$0$};
            \node (100) at (10,0) {$100$};
            \draw [thick] (0) -- (100);
            \node [below] at (6.7,0) {$67$};

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../data/histogram_of_guesses.pdf}
        \caption{Frequency of guesses depending on the round of play.}
        \label{fig:histogram_of_guess}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../data/jointplot_of_guesses.pdf}
        \caption{Linear relationship between guesses of each round of play.}
        \label{fig:jointplot_of_guess}
    \end{subfigure}
    \caption{Results from all data collected.}
    \label{fig:all_results}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../data/histogram_of_guesses_removing_increasing_guesses.pdf}
        \caption{Frequency of guesses depending on the round of play.}
        \label{fig:histogram_of_guess}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../data/jointplot_of_guesses_removing_increasing_guesses.pdf}
        \caption{Linear relationship between guesses of each round of play.}
        \label{fig:jointplot_of_guess}
    \end{subfigure}
    \caption{Results from data when removing increasing guesses.}
    \label{fig:results_with_decreasing_guess}
\end{figure}

@@

@@

Without realising it the participants have described a well known strategy
(\textbf{Grudger}) which takes in to account the entire history of play.
Figure \ref{fig:} shows a photo of a final board for a particular implementation
of this activity.

This activity can be complemented with a demonstration of software that allows
for the rapid simulation of Axelrod's tournament \cite{Knight2015}. Figure
\ref{fig:evolutionary_axelrod} shows the performance of the strategies when put
in an evolutionary context.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.6\textwidth]{static/basic_strategies-reproduce.pdf}
    \caption{Repeated games in an evolutionary context}
    \label{fig:evolutionary_axelrod}
\end{figure}

Weakness about all participants observing...

As well as being enjoyable this activity is a good intro to...

Furthermore can be modified to study ...

>>>>

\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true]{biblatex}
\addbibresource{library.bib}

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[thick,scale=0.7, every node/.style={scale=0.7}]
            % First level of play
            \node (0) at (0,0) {$0$};
            \node (100) at (10,0) {$100$};
            \draw [thick] (0) -- (100);
            \node [below] at (6.7,0) {$67$};

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{static/histogram_of_guesses.pdf}
        \caption{Frequency of guesses depending on the round of play.}
        \label{fig:histogram_of_guess}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{static/jointplot_of_guesses.pdf}
        \caption{Linear relationship between guesses of each round of play.}
        \label{fig:jointplot_of_guess}
    \end{subfigure}
    \caption{Results from all data collected.}
    \label{fig:all_results}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{static/histogram_of_guesses_removing_increasing_guesses.pdf}
        \caption{Frequency of guesses depending on the round of play.}
        \label{fig:histogram_of_guess}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{static/jointplot_of_guesses_removing_increasing_guesses.pdf}
        \caption{Linear relationship between guesses of each round of play.}
        \label{fig:jointplot_of_guess}
    \end{subfigure}
    \caption{Results from data when removing increasing guesses.}
    \label{fig:results_with_decreasing_guess}
\end{figure}

@@

Figure \ref{fig:white_board} shows a photo of a final board for a particular
implementation of this activity.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.5\textwidth]{static/white_board.jpg}
    \caption{A photo of an actual implementation of the tournament.}
    \label{fig:white_board}
\end{figure}

@@

Without realising it the participants have described a well known strategy
(\textbf{Grudger}) which takes in to account the entire history of play.

This activity can be complemented with a demonstration of software that allows
for the rapid simulation of Axelrod's tournament
\cite{Axelrod-Pythonprojectteam2015}. Figure \ref{fig:evolutionary_axelrod}
shows the performance of the strategies when put in an evolutionary context.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.6\textwidth]{static/basic_strategies-reproduce.pdf}
    \caption{Repeated games in an evolutionary context.}
    \label{fig:evolutionary_axelrod}
\end{figure}

One of the weaknesses of this approach is that all participants observe the play
by all the teams. Whilst from a mathematical perspective reputation is inferred
to mean the reputation gained during a particular duel, this has the effect of
teams being able to observe how other teams seem to play. A true replication of
Axelrod's tournament would not allow for this. One possibility would invite
participants to leave the room which might be logistically constrained. From a
pedagogic point of view however, having participants observe the duels often
leads to a much more engaged discussion (after as well as during the activity).

This activity is usually very enjoyable and leads to a lively discussion.
Further to the fun had by participants, the theoretic discussion about repeated
games can be placed in the exact context of the tournament that was just played.

This tournament can be used to introduce further game theoretic topics with
slight modifications:

\begin{itemize}
    \item \textbf{Infinitely repeated games with discounting}: the discount
        factor can be interpreted as a probability of the duel continuing for
        another round (this can be randomly sampled).
    \item \textbf{Markov games}: the two random game states can be a true game
        and an absorbing game so that this corresponds to an infinite game with
        discounting.
    \item \textbf{Evolutionary games}: the two random game states can be a true game
        and an absorbing game so that this corresponds to an infinite game with
        discounting.
\end{itemize}
